\documentclass[a4paper]{article}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage[table]{xcolor}
\begin{document}
\title{Pylux User Manual \\ \large{for Pylux v0.1.0}}
\author{J. Page}
\date{2016}
\maketitle
\vspace{1.0pt}
Copyright (C)  2015 2016 Jack Page \\
Permission is granted to copy, distribute and/or modify this document
in source form (LaTeX) or compiled form (PDF, PostScript, etc.), including 
for commercial use, provided that this copyright notice is retained and that 
you grant the same freedoms to any recipients of your modifications.
\tableofcontents
\newpage
% ------- END HEADER MATERIAL ------- %
\section{Introduction}
\subsection{About Pylux}
Pylux is a program written in Python for the manipulation of XML plot files. 
These plot files can contain information about fixtures, cues, scenes and DMX 
universes. 

Pylux can create SVG diagrams of lighting plots and documentation using 
Jinja2 templates.

Bugs and feature requests should be submitted to 
\url{https://github.com/jackdpage/pylux/issues}.

\subsection{About this Manual}
This manual is intended for general users of Pylux. If you are a developer 
who wants to contribute to Pylux, you should read the Developer Reference. 
The first section of this manual details all of the actions that you can enter 
on the command-line interface of Pylux. The second section goes into more 
detail about what tags you should use, etc.

% ------- USER SECTION ------- %
\section{Command-line Options}
Pylux is invoked simply by running the \texttt{pylux} package with Python. 

\paragraph{\texttt{--help}, \texttt{-h}}
Display the usage message of the program then exit.

\paragraph{\texttt{--version}, \texttt{-v}}
Display the version number of the program then exit.

\paragraph{\texttt{--file \textit{FILE}}, \texttt{-f \textit{FILE}}} 
Load the file with path \texttt{\textit{FILE}} as the plot file on launch.

\paragraph{\texttt{--gui}, \texttt{-g}}
Launch Pylux with the graphical user interface. This is not yet implemented. 
Omitting this flag launches Pylux with its standard CLI interface.

\paragraph{\texttt{--verbose}, \texttt{-V}}
Set the verbosity level of output. Don't include to keep logging level at the 
default of \texttt{WARNING}. Include once for logging level of \texttt{INFO} 
and include twice for a logging level of \texttt{DEBUG}.

\section{Using the Command Line Interface}
The command line interface (CLI) is the default interface used by Pylux. It 
allows for very efficient editing of plot files with very little CPU overhead. 

The CLI is interacted with using a series of commands, each of which may have 
one or more arguments. When the prompt is displayed, the program is waiting 
for the user to enter one of these commands. Each command is a memorable 
two character sequence (apart from the utility commands), where the first 
character is the object that is going to be acted upon and the second 
character is the action to perform.

\subsection{Piping Complex Objects into Commands}
Many commands require that you specify an object other than one which can be 
represented by a simple command line string. For example, the \texttt{xs} 
command requires that you supply a fixture object as an argument. This is made 
possible whilst retaining the simplicity of text based entry through the 
interface reference system.

When you run a listing or filtering command such as \texttt{xl}, you will 
notice that the objects in the list each have a number which is underlined. 
This is that objects's interface reference. Using this, you can pipe objects
into other commands, simply by specifying the number where the command calls 
for another object type. 

To allow for the efficient manipulation of objects in batch, you can specify 
more than one object at once using a comma-separated list (provided of course 
that the command allows for multiple objects to be piped into it) such as 
\texttt{a,b,c}. You can also specify ranges of numbers if you are piping 
sequential objects from a list using the format \texttt{a:b} where \texttt{a} 
and \texttt{b} are the inclusive limits. You can of course use any 
combination of these formats, such as \texttt{a:b,c,d:e,f}.

If you need to pipe the same object or group of objects into multiple commands, 
you can use the \texttt{this} reference instead of a number or list of numbers. 
This points to the last used reference, so will pipe in the same object or 
objects that were used for the last command, unless the reference list has 
changed since (i.e. a listing command has been run again).

\subsection{Contexts}
Pylux has too many functions to be able to have a sensible two character 
mnemonic for every command. For that reason, Pylux uses a system of contexts 
to facilitate its growing command list.

Essentially, using a context is just like loading a different command list. 
Your current context is indicated by the prompt, contexts  will have the 
prompt \texttt{(pylux:\textit{CONTEXT})}. To enter a different context, use 
the command \texttt{:\textit{CONTEXT}}. To escape from the current context 
to the default context, type \texttt{::}.

You can specify the default context in the configuration file. By default it 
is \texttt{editor}.

There are some commands which are available in all contexts, for ease of 
access:

\paragraph{\texttt{c}}
Clears the screen of previous input and output. This uses the system screen 
clearing command. (\texttt{clear} on UNIX, \texttt{cls} on Windows)

\paragraph{\texttt{Q}}
Exit the program without saving any changes to disk.

\subsection{The \texttt{editor} Context}
The \texttt{editor} context is used to directly edit the contents of the 
plot files. It does not produce any useful output and is just used to edit 
plot files to feed into other contexts for processing.

\subsubsection{File Commands}

\paragraph{\texttt{fo \textit{FILE}}}
Open the file with path \texttt{\textit{FILE}} as the plot file. This will 
override any unsaved buffer associated with the previous plot file, if 
there was one.

\paragraph{\texttt{fw}}
Save the current file buffer to its original location.

\paragraph{\texttt{fW \textit{PATH}}}
Save the current file buffer to a new file with location 
\texttt{\textit{PATH}}.

\paragraph{\texttt{fg}}
Print the path of the file that is currently loaded.

\paragraph{\texttt{fn \textit{PATH}}}
Create an new empty plot file at the location with path \texttt{\textit{PATH}} 
and load it as the new plot file

\subsubsection{Metadata Commands}

\paragraph{\texttt{mG}}
List all the metadata tags associated with the currently loaded plot file.

\paragraph{\texttt{ms \textit{TAG VALUE}}}
Set the value of the metadata with tag \texttt{\textit{TAG}} to 
\texttt{\textit{VALUE}}. If the metadata already exists, it will be 
overridden.

\paragraph{\texttt{mr \textit{TAG}}}
Remove the piece of metadata from the file which has the name 
\texttt{\textit{TAG}}.

\paragraph{\texttt{mg \textit{TAG}}}
Get the value of a piece of metadata. Prints the value of the metadata with
name \texttt{\textit{TAG}} on the screen.

\subsubsection{Fixture Commands}

\paragraph{\texttt{xn \textit{TEMPLATE}}}
Add a new fixture to the plot. This will load the contents of the fixture 
file with the name \texttt{TEMPLATE} into the new fixture, including DMX 
functions. This will not allocate DMX addresses to the fixture, use 
\texttt{xA} for that.

\paragraph{\texttt{xc \textit{REF}}}
Clone the fixture with interface reference \texttt{\textit{REF}} into a new 
fixture. This does not reassign any DMX values.

\paragraph{\texttt{xl}}
List all the fixtures in the plot. This will generate a list of every fixture 
in the plot, listing an interface reference, the fixture olid, and the fixture 
UUID.

\paragraph{\texttt{xf \textit{TAG VALUE}}}
List all the fixtures in the plot which have a tag called 
\texttt{\textit{TAG}} with a value of \texttt{\textit{VALUE}}. Like the list 
function, this will list an interface reference, the fixture olid and UUID, 
and also the value of the tag that was given for verification purposes.

\paragraph{\texttt{xg \textit{REF TAG}}}
Print the value of \texttt{\textit{TAG}} for the fixture with interface
reference \texttt{\textit{REF}}.

\paragraph{\texttt{xG \textit{REF}}}
List all the information associated with the fixture with interface reference 
\texttt{\textit{REF}}.

\paragraph{\texttt{xr \textit{REF}}}
Remove the fixture with the interface reference \texttt{\textit{REF}}. This 
fixture will be removed from the plot, but associated DMX channels will not be 
removed, use \texttt{xp} for that.

\paragraph{\texttt{xs \textit{REF TAG VALUE}}}
Set the value of \texttt{\textit{TAG}} in fixture with interface reference 
\texttt{\textit{REF}} to \texttt{\textit{VALUE}}. For a list of standard 
fixture tags, see \autoref{sec:fixtags}. There are also some shortcuts to set 
mulitple tags at once, which can be found in the pseudo tags section.

\paragraph{\texttt{xa \textit{REF UNIVERSE ADDR}}}
Assign DMX addresses to the fixture with interface reference 
\texttt{\textit{REF}}. This will add the fixture to the universe 
\texttt{\textit{UNIVERSE}}, beginning at the start address 
\texttt{\textit{ADDR}}. \texttt{\textit{ADDR}} can either be a user-assigned 
number or auto to allow Pylux to choose the most appropriate start address.

\paragraph{\texttt{xp \textit{REF}}}
Remove the fixture with interface reference \texttt{\textit{REF}} from the 
plot and also remove any DMX channels associated with it.

\subsubsection{DMX Registry Commands}

\paragraph{\texttt{rl \textit{UNIVERSE}}}
List all the used channels in \texttt{\textit{UNIVERSE}}. This will list the 
DMX address, fixture UUID and function of every channel in the DMX registry 
with identifier \texttt{\textit{UNIVERSE}}.

\subsubsection{Cue Commands}

\paragraph{\texttt{qn \textit{TYPE LOCATION}}}
Append a cue to the cue list. Set the type to \texttt{\textit{TYPE}} which is 
either \texttt{LX}, \texttt{SX} or \texttt{VX} and the \texttt{location} tag 
to \texttt{\textit{LOCATION}}. \texttt{\textit{LOCATION}} is the cue line or 
visual in the script.

\paragraph{\texttt{ql}}
List all the cues in the cue list, listing their type, location and sort key.

\paragraph{\texttt{qs \textit{CUE TAG VALUE}}}
Set the value of \texttt{\textit{TAG}} to \texttt{\textit{VALUE}} for 
\texttt{\textit{CUE}}, where \texttt{\textit{CUE}} is an interface reference 
list.

\paragraph{\texttt{qg \textit{CUE TAG}}}
Print the value of \texttt{\textit{TAG}} for \texttt{\textit{CUE}}.

\paragraph{\texttt{qG \textit{CUE}}}
Print the value of all tags for \texttt{\textit{CUE}}.

\paragraph{\texttt{qr \textit{CUE}}}
Remove \texttt{\textit{CUE}} from the cue list.

\paragraph{\texttt{qm \textit{CUE AFTER}}}
Adjust the sort keys of the cues so that \texttt{\textit{CUE}} comes 
immediately after the cue \texttt{\textit{AFTER}} in the cue list.

\paragraph{\texttt{qM \textit{CUE BEFORE}}}
Adjust the sort keys of the cues so that \texttt{\textit{CUE}} comes 
immediately before the cue \texttt{\textit{BEFORE}} in the cue list.

\subsection{The \texttt{plotter} Context}
The \texttt{plotter} context is used to produce 2D SVG representations of the 
plot. It does this using the position and focus data associated with fixtures, 
as well as gel colours.

\subsubsection{Commands}

\paragraph{\texttt{pn}}
Generates a new SVG plot from the current plot file and options. The file is 
saved internally.

\paragraph{\texttt{pw \textit{PATH}}}
Write the internal plot buffer to \texttt{\textit{PATH}}.

\paragraph{\texttt{os \textit{OPTION VALUE}}}
Set the value of the option with name \texttt{\textit{OPTION}} to 
\texttt{\textit{VALUE}}.

\paragraph{\texttt{og \textit{OPTION}}}
Print the value of \texttt{\textit{OPTION}} to the console.

\paragraph{\texttt{oG}}
Print the values of all the options.

\subsubsection{Options}

\paragraph{\texttt{beam\_colour}}
The colour of the beam focus lines. Can be any colour in the legal list of 
gel colours or \texttt{auto} to make the focus lines the same colour as the 
fixture from which they come. Default: \texttt{Black}.

\paragraph{\texttt{beam\_width}}
The thickness of the beam focus lines in SVG points. Default: \texttt{6}.

\paragraph{\texttt{show\_beams}}
Choose whether or not to display the beam focus lines. Must be \texttt{True} 
or \texttt{False}. Default: \texttt{True}.

\subsection{The \texttt{reporter} Context}
The \texttt{reporter} context is used to create various types of 
documentation from Jinja2 templates.

\subsubsection{Commands}

\paragraph{\texttt{rn \textit{TEMPLATE}}}
Generates a report using the template \texttt{\textit{TEMPLATE}}. 

\paragraph{\texttt{rw \textit{PATH}}}
Write the contents of the internal report buffer to \texttt{\textit{PATH}}.

% -------- FILES SECTION ------- %
\section{Standard Tags} \label{sec:plotfile}
Below is a list of standard tags for each section, to advise which tags you 
should apply to your metadata and fixtures. Also included is a list of 
pseudo-tags: tags which are not added to the file but actually represent one 
or more other tags to make adding them easier.

\subsection{Standard Metadata Tags}
Whilst you can use any name for a tag you wish, there are some standard ones 
which are used by Pylux and its bundled extensions.

\paragraph{\texttt{production}}
The name of the production for which the lighting documentation is being 
produced, e.g. 'Romeo and Juliet'. Used by: \texttt{texlux}.

\paragraph{\texttt{designer}}
The name of the lighting designer for this production. Used by: 
\texttt{texlux}.

\paragraph{\texttt{board\_operator}}
The name of the person operating the main lighting board for this production.
Used by: \texttt{texlux}.

\paragraph{\texttt{spot\_operator}}
The name of the person operating the primary followspot for this production.
Used by: \texttt{texlux}.

\paragraph{\texttt{director}}
The name of the director of the production. Used by: \texttt{texlux}.

\paragraph{\texttt{venue}}
The location at which the production is taking place. Used by: 
\texttt{texlux}.

\subsection{Standard Fixture Data Tags} \label{sec:fixtags}

\paragraph{\texttt{dmx\_functions}}
This is the parent of a list of empty elements, each of which represents a 
function that the fixture has that requires the use of a DMX channel. For 
example, traditional fixtures will have an \texttt{intensity} function 
whilst modern LED fixtures may have \texttt{colour} and \texttt{mode} 
functions.

\paragraph{\texttt{dmx\_channels}}
The number of DMX channels that a fixture needs. This is automatically 
calculated from the \texttt{dmx\_functions} tag, so should not be changed 
manually.

\paragraph{\texttt{dmx\_start\_address}}
The start address of this fixture, if it has been addressed. This is 
automatically assigned using the address function so shouldn't be changed 
manually.

\paragraph{\texttt{universe}}
The universe in which the DMX channels for this fixture are located. This too 
is set when the address command is run so shouldn't be changed by the user. 

\paragraph{\texttt{posX}}
The x position in 2D space where this fixture is located. Measured in metres.

\paragraph{\texttt{posY}}
The y position in 2D space where this fixture is located. Measured in metres.

\paragraph{\texttt{focusX}}
The x position in 2D space where the centre of this fixture's beam is 
focused. Measured in metres.

\paragraph{\texttt{focusY}}
The y position in 2D space where the centre of this fixture's beam is 
focused. Measured in metres.

\paragraph{\texttt{rotation}}
The rotation of this fixture about its centre. Measured anticlockwise from 
the positive x axis in degrees. This can be automatically calculated if the 
preceding four data tags are present.

\paragraph{\texttt{circuit}}
For traditional fixtures only. The circuit into which the fixture is patched. 
Used by: \texttt{texlux}.

\paragraph{\texttt{power}}
For traditional fixtures only. The maximum power draw by the lamp in this 
fixture.

\paragraph{\texttt{dimmer\_uuid}}
For traditional fixtures only. The UUID of the dimmer (which must exist as a 
separate fixture in the plot file) which is controlling this fixture.

\paragraph{\texttt{dimmer\_chan}}
For traditional fixtures only. The name or number of the dimmer channel by 
which this fixture is controlled. 

\paragraph{\texttt{gel}}
The manufacturer's code of the gel that is being used in this fixture. The 
automatic colour calculation currently supports Rosco Supergel and E-colour 
and the named HTML (X11) colours.

\paragraph{\texttt{colour}}
A hexadecimal colour code indicating the colour which best represents the gel 
in this fixture. Can be automatically calculated if gel is present.

\subsection{Pseudo Fixture Tags}
These tags can be used to set multiple attributes of a fixture at once.

\paragraph{\texttt{position \textit{X},\textit{Y}}}
Sets \texttt{posX} to \texttt{\textit{X}} and \texttt{posY} to 
\texttt{\textit{Y}}.

\paragraph{\texttt{focus \textit{X},\textit{Y}}}
Sets \texttt{focusX} to \texttt{\textit{X}} and \texttt{focusY} to 
\texttt{\textit{Y}}.

\paragraph{\texttt{dimmer \textit{REF} \textit{CHAN}}}
Sets \texttt{dimmer\_uuid} to the uuid of the dimmer represented by 
\texttt{\textit{REF}} and \texttt{dimmer\_channel} to \texttt{\textit{CHAN}}.

\subsection{Standard Cue Tags}
Cues are different to fixtures in that their order is important. Pylux can't 
tell which order cues should go in based on the cue line, and it doesn't 
understand page numbers. Therefore, each cue has a special attributed called 
\texttt{key} which determines which order it goes in in the cue list. Use the 
\texttt{qm} and \texttt{qM} commands to manipulate keys.

\paragraph{\texttt{type}}
The type of cue, either \texttt{LX}, \texttt{SX} or \texttt{VX}.

\paragraph{\texttt{location}}
The cue in the script, could be a line or visual cue.

\paragraph{\texttt{description}}
A human-readable description of what should happen.

\paragraph{\texttt{scene}}
If this is a lighting cue, the UUID of the scene which is used for it.

\appendix
\section{Included Templates}
For any template file that Pylux uses, you can use your own, but it comes 
with a few to get you started.

\subsection{Fixture Templates}
\begin{longtable}{|l|r|}
\hline
Fixture Type & Pylux Short Name \\ \hline
Generic Incandescent & generic \\
Hutton P650 & p650 \\
LEDJ RGB PAR & ledjrgbpar \\
PAR64 MFL & par64mfl \\
Strand Patt.23 & patt23 \\
Zero88 Betapack 2 & betapack2 \\
\hline
\end{longtable}

\subsection{Jinja Templates}
\begin{longtable}{|l|l|}
\hline
Template Name & Format \\ \hline
cuelist & .tex \\
dimmerlist & .tex \\
\hline
\end{longtable}

\section{Supported Gel Colours}
These are the gel names that can be assigned to a fixture and their colour be 
generated automatically.

\subsection{HTML Standard Colours}
Standard HTML/X11 named colours. Taken directly from the HTML colour 
definitions.
\begin{longtable}{|l|r|}
\hline
Colour Name & Rendered Colour \\ \hline
AliceBlue & \texttt{\#F0F8FF} \cellcolor[HTML]{F0F8FF} \\
AntiqueWhite & \texttt{\#FAEBD7} \cellcolor[HTML]{FAEBD7} \\
Aqua & \texttt{\#00FFFF} \cellcolor[HTML]{00FFFF} \\
Aquamarine & \texttt{\#7FFFD4} \cellcolor[HTML]{7FFFD4} \\
Azure & \texttt{\#F0FFFF} \cellcolor[HTML]{F0FFFF} \\
Beige & \texttt{\#F5F5DC} \cellcolor[HTML]{F5F5DC} \\
Bisque & \texttt{\#FFE4C4} \cellcolor[HTML]{FFE4C4} \\
Black & \texttt{\#000000} \cellcolor[HTML]{000000} \\
BlanchedAlmond & \texttt{\#FFEBCD} \cellcolor[HTML]{FFEBCD} \\
Blue & \texttt{\#0000FF} \cellcolor[HTML]{0000FF} \\
BlueViolet & \texttt{\#8A2BE2} \cellcolor[HTML]{8A2BE2} \\
Brown & \texttt{\#A52A2A} \cellcolor[HTML]{A52A2A} \\
BurlyWood & \texttt{\#DEB887} \cellcolor[HTML]{DEB887} \\
CadetBlue & \texttt{\#5F9EA0} \cellcolor[HTML]{5F9EA0} \\
Chartreuse & \texttt{\#7FFF00} \cellcolor[HTML]{7FFF00} \\
Chocolate & \texttt{\#D2691E} \cellcolor[HTML]{D2691E} \\
Coral & \texttt{\#FF7F50} \cellcolor[HTML]{FF7F50} \\
CornflowerBlue & \texttt{\#6495ED} \cellcolor[HTML]{6495ED} \\
Cornsilk & \texttt{\#FFF8DC} \cellcolor[HTML]{FFF8DC} \\
Crimson & \texttt{\#DC143C} \cellcolor[HTML]{DC143C} \\
Cyan & \texttt{\#00FFFF} \cellcolor[HTML]{00FFFF} \\
DarkBlue & \texttt{\#00008B} \cellcolor[HTML]{00008B} \\
DarkCyan & \texttt{\#008B8B} \cellcolor[HTML]{008B8B} \\
DarkGoldenrod & \texttt{\#B8860B} \cellcolor[HTML]{B8860B} \\
DarkGray & \texttt{\#A9A9A9} \cellcolor[HTML]{A9A9A9} \\
DarkGreen & \texttt{\#006400} \cellcolor[HTML]{006400} \\
DarkKhaki & \texttt{\#BDB76B} \cellcolor[HTML]{BDB76B} \\
DarkMagenta & \texttt{\#8B008B} \cellcolor[HTML]{8B008B} \\
DarkOliveGreen & \texttt{\#556B2F} \cellcolor[HTML]{556B2F} \\
DarkOrange & \texttt{\#FF8C00} \cellcolor[HTML]{FF8C00} \\
DarkOrchid & \texttt{\#9932CC} \cellcolor[HTML]{9932CC} \\
DarkRed & \texttt{\#8B0000} \cellcolor[HTML]{8B0000} \\
DarkSalmon & \texttt{\#E9967A} \cellcolor[HTML]{E9967A} \\
DarkSeaGreen & \texttt{\#8FBC8F} \cellcolor[HTML]{8FBC8F} \\
DarkSlateBlue & \texttt{\#483D8B} \cellcolor[HTML]{483D8B} \\
DarkSlateGray & \texttt{\#2F4F4F} \cellcolor[HTML]{2F4F4F} \\
DarkTurquoise & \texttt{\#00CED1} \cellcolor[HTML]{00CED1} \\
DarkViolet & \texttt{\#9400D3} \cellcolor[HTML]{9400D3} \\
DeepPink & \texttt{\#FF1493} \cellcolor[HTML]{FF1493} \\
DeepSkyBlue & \texttt{\#00BFFF} \cellcolor[HTML]{00BFFF} \\
DimGray & \texttt{\#696969} \cellcolor[HTML]{696969} \\
DodgerBlue & \texttt{\#1E90FF} \cellcolor[HTML]{1E90FF} \\
FireBrick & \texttt{\#B22222} \cellcolor[HTML]{B22222} \\
FloralWhite & \texttt{\#FFFAF0} \cellcolor[HTML]{FFFAF0} \\
ForestGreen & \texttt{\#228B22} \cellcolor[HTML]{228B22} \\
Fuchsia & \texttt{\#FF00FF} \cellcolor[HTML]{FF00FF} \\
Gainsboro & \texttt{\#DCDCDC} \cellcolor[HTML]{DCDCDC} \\
GhostWhite & \texttt{\#F8F8FF} \cellcolor[HTML]{F8F8FF} \\
Gold & \texttt{\#FFD700} \cellcolor[HTML]{FFD700} \\
Goldenrod & \texttt{\#DAA520} \cellcolor[HTML]{DAA520} \\
Gray & \texttt{\#808080} \cellcolor[HTML]{808080} \\
Green & \texttt{\#008000} \cellcolor[HTML]{008000} \\
GreenYellow & \texttt{\#ADFF2F} \cellcolor[HTML]{ADFF2F} \\
Honeydew & \texttt{\#F0FFF0} \cellcolor[HTML]{F0FFF0} \\
HotPink & \texttt{\#FF69B4} \cellcolor[HTML]{FF69B4} \\
IndianRed & \texttt{\#CD5C5C} \cellcolor[HTML]{CD5C5C} \\
Indigo & \texttt{\#4B0082} \cellcolor[HTML]{4B0082} \\
Ivory & \texttt{\#FFFFF0} \cellcolor[HTML]{FFFFF0} \\
Khaki & \texttt{\#F0E68C} \cellcolor[HTML]{F0E68C} \\
Lavender & \texttt{\#E6E6FA} \cellcolor[HTML]{E6E6FA} \\
LavenderBlush & \texttt{\#FFF0F5} \cellcolor[HTML]{FFF0F5} \\
LawnGreen & \texttt{\#7CFC00} \cellcolor[HTML]{7CFC00} \\
LemonChiffon & \texttt{\#FFFACD} \cellcolor[HTML]{FFFACD} \\
LightBlue & \texttt{\#ADD8E6} \cellcolor[HTML]{ADD8E6} \\
LightCoral & \texttt{\#F08080} \cellcolor[HTML]{F08080} \\
LightCyan & \texttt{\#E0FFFF} \cellcolor[HTML]{E0FFFF} \\
LightGoldenrodYellow & \texttt{\#FAFAD2} \cellcolor[HTML]{FAFAD2} \\
LightGreen & \texttt{\#90EE90} \cellcolor[HTML]{90EE90} \\
LightGrey & \texttt{\#D3D3D3} \cellcolor[HTML]{D3D3D3} \\
LightPink & \texttt{\#FFB6C1} \cellcolor[HTML]{FFB6C1} \\
LightSalmon & \texttt{\#FFA07A} \cellcolor[HTML]{FFA07A} \\
LightSeaGreen & \texttt{\#20B2AA} \cellcolor[HTML]{20B2AA} \\
LightSkyBlue & \texttt{\#87CEFA} \cellcolor[HTML]{87CEFA} \\
LightSlateGray & \texttt{\#778899} \cellcolor[HTML]{778899} \\
LightSteelBlue & \texttt{\#B0C4DE} \cellcolor[HTML]{B0C4DE} \\
LightYellow & \texttt{\#FFFFE0} \cellcolor[HTML]{FFFFE0} \\
Lime & \texttt{\#00FF00} \cellcolor[HTML]{00FF00} \\
LimeGreen & \texttt{\#32CD32} \cellcolor[HTML]{32CD32} \\
Linen & \texttt{\#FAF0E6} \cellcolor[HTML]{FAF0E6} \\
Magenta & \texttt{\#FF00FF} \cellcolor[HTML]{FF00FF} \\
Maroon & \texttt{\#800000} \cellcolor[HTML]{800000} \\
MediumAquamarine & \texttt{\#66CDAA} \cellcolor[HTML]{66CDAA} \\
MediumBlue & \texttt{\#0000CD} \cellcolor[HTML]{0000CD} \\
MediumOrchid & \texttt{\#BA55D3} \cellcolor[HTML]{BA55D3} \\
MediumPurple & \texttt{\#9370DB} \cellcolor[HTML]{9370DB} \\
MediumSeaGreen & \texttt{\#3CB371} \cellcolor[HTML]{3CB371} \\
MediumSlateBlue & \texttt{\#7B68EE} \cellcolor[HTML]{7B68EE} \\
MediumSpringGreen & \texttt{\#00FA9A} \cellcolor[HTML]{00FA9A} \\
MediumTurquoise & \texttt{\#48D1CC} \cellcolor[HTML]{48D1CC} \\
MediumVioletRed & \texttt{\#C71585} \cellcolor[HTML]{C71585} \\
MidnightBlue & \texttt{\#191970} \cellcolor[HTML]{191970} \\
MintCream & \texttt{\#F5FFFA} \cellcolor[HTML]{F5FFFA} \\
MistyRose & \texttt{\#FFE4E1} \cellcolor[HTML]{FFE4E1} \\
Moccasin & \texttt{\#FFE4B5} \cellcolor[HTML]{FFE4B5} \\
NavajoWhite & \texttt{\#FFDEAD} \cellcolor[HTML]{FFDEAD} \\
Navy & \texttt{\#000080} \cellcolor[HTML]{000080} \\
OldLace & \texttt{\#FDF5E6} \cellcolor[HTML]{FDF5E6} \\
Olive & \texttt{\#808000} \cellcolor[HTML]{808000} \\
OliveDrab & \texttt{\#6B8E23} \cellcolor[HTML]{6B8E23} \\
Orange & \texttt{\#FFA500} \cellcolor[HTML]{FFA500} \\
OrangeRed & \texttt{\#FF4500} \cellcolor[HTML]{FF4500} \\
Orchid & \texttt{\#DA70D6} \cellcolor[HTML]{DA70D6} \\
PaleGoldenrod & \texttt{\#EEE8AA} \cellcolor[HTML]{EEE8AA} \\
PaleGreen & \texttt{\#98FB98} \cellcolor[HTML]{98FB98} \\
PaleTurquoise & \texttt{\#AFEEEE} \cellcolor[HTML]{AFEEEE} \\
PaleVioletRed & \texttt{\#DB7093} \cellcolor[HTML]{DB7093} \\
PapayaWhip & \texttt{\#FFEFD5} \cellcolor[HTML]{FFEFD5} \\
PeachPuff & \texttt{\#FFDAB9} \cellcolor[HTML]{FFDAB9} \\
Peru & \texttt{\#CD853F} \cellcolor[HTML]{CD853F} \\
Pink & \texttt{\#FFC0CB} \cellcolor[HTML]{FFC0CB} \\
Plum & \texttt{\#DDA0DD} \cellcolor[HTML]{DDA0DD} \\
PowderBlue & \texttt{\#B0E0E6} \cellcolor[HTML]{B0E0E6} \\
Purple & \texttt{\#800080} \cellcolor[HTML]{800080} \\
Red & \texttt{\#FF0000} \cellcolor[HTML]{FF0000} \\
RosyBrown & \texttt{\#BC8F8F} \cellcolor[HTML]{BC8F8F} \\
RoyalBlue & \texttt{\#4169E1} \cellcolor[HTML]{4169E1} \\
SaddleBrown & \texttt{\#8B4513} \cellcolor[HTML]{8B4513} \\
Salmon & \texttt{\#FA8072} \cellcolor[HTML]{FA8072} \\
SandyBrown & \texttt{\#F4A460} \cellcolor[HTML]{F4A460} \\
SeaGreen & \texttt{\#2E8B57} \cellcolor[HTML]{2E8B57} \\
Seashell & \texttt{\#FFF5EE} \cellcolor[HTML]{FFF5EE} \\
Sienna & \texttt{\#A0522D} \cellcolor[HTML]{A0522D} \\
Silver & \texttt{\#C0C0C0} \cellcolor[HTML]{C0C0C0} \\
SkyBlue & \texttt{\#87CEEB} \cellcolor[HTML]{87CEEB} \\
SlateBlue & \texttt{\#6A5ACD} \cellcolor[HTML]{6A5ACD} \\
SlateGray & \texttt{\#708090} \cellcolor[HTML]{708090} \\
Snow & \texttt{\#FFFAFA} \cellcolor[HTML]{FFFAFA} \\
SpringGreen & \texttt{\#00FF7F} \cellcolor[HTML]{00FF7F} \\
SteelBlue & \texttt{\#4682B4} \cellcolor[HTML]{4682B4} \\
Tan & \texttt{\#D2B48C} \cellcolor[HTML]{D2B48C} \\
Teal & \texttt{\#008080} \cellcolor[HTML]{008080} \\
Thistle & \texttt{\#D8BFD8} \cellcolor[HTML]{D8BFD8} \\
Tomato & \texttt{\#FF6347} \cellcolor[HTML]{FF6347} \\
Turquoise & \texttt{\#40E0D0} \cellcolor[HTML]{40E0D0} \\
Violet & \texttt{\#EE82EE} \cellcolor[HTML]{EE82EE} \\
Wheat & \texttt{\#F5DEB3} \cellcolor[HTML]{F5DEB3} \\
White & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
WhiteSmoke & \texttt{\#F5F5F5} \cellcolor[HTML]{F5F5F5} \\
Yellow & \texttt{\#FFFF00} \cellcolor[HTML]{FFFF00} \\
YellowGreen & \texttt{\#9ACD32} \cellcolor[HTML]{9ACD32} \\
\hline
\end{longtable}

\subsection{Rosco Gels}
Colour representations taken from The official Rosco website. Both the gel name 
and manufacturer code can be used. E-Colour+ gels have an R prefixed to their 
manufacturer code, Supergel gels have an S prefixed to their manufacturer code.
\subsubsection{E-Colour+}
\begin{longtable}{|l|l|r|}
\hline
Gel Name & Manufacturer Code & Rendered Colour \\ \hline
Rose Pink & R002 & \texttt{\#FF40B9} \cellcolor[HTML]{FF40B9} \\
Lavender Tint & R003 & \texttt{\#F5E6FF} \cellcolor[HTML]{F5E6FF} \\
Medium Bastard Amber & R004 & \texttt{\#FAB8AC} \cellcolor[HTML]{FAB8AC} \\
Pale Yellow & R007 & \texttt{\#FFFFDE} \cellcolor[HTML]{FFFFDE} \\
Dark Salmon & R008 & \texttt{\#FF5E48} \cellcolor[HTML]{FF5E48} \\
Pale Amber Gold & R009 & \texttt{\#FFD28A} \cellcolor[HTML]{FFD28A} \\
Medium Yellow & R010 & \texttt{\#FFF30D} \cellcolor[HTML]{FFF30D} \\
Straw Tint & R013 & \texttt{\#FFDBA1} \cellcolor[HTML]{FFDBA1} \\
Deep Straw & R015 & \texttt{\#FDC819} \cellcolor[HTML]{FDC819} \\
Surprise Peach & R017 & \texttt{\#CC5F3D} \cellcolor[HTML]{CC5F3D} \\
Fire & R019 & \texttt{\#ED2000} \cellcolor[HTML]{ED2000} \\
Medium Amber & R020 & \texttt{\#FF8A24} \cellcolor[HTML]{FF8A24} \\
Gold Amber & R021 & \texttt{\#FF4800} \cellcolor[HTML]{FF4800} \\
Dark Amber & R022 & \texttt{\#FF1900} \cellcolor[HTML]{FF1900} \\
Scarlet & R024 & \texttt{\#F00E25} \cellcolor[HTML]{F00E25} \\
Sunset Red & R025 & \texttt{\#FF4B2B} \cellcolor[HTML]{FF4B2B} \\
Bright Red & R026 & \texttt{\#C70011} \cellcolor[HTML]{C70011} \\
Medium Red & R027 & \texttt{\#A10000} \cellcolor[HTML]{A10000} \\
Plasa Red & R029 & \texttt{\#BC0010} \cellcolor[HTML]{BC0010} \\
Light Pink & R035 & \texttt{\#FFB8CE} \cellcolor[HTML]{FFB8CE} \\
Medium Pink & R036 & \texttt{\#FF6E9E} \cellcolor[HTML]{FF6E9E} \\
Pink Carnation & R039 & \texttt{\#FAC0D8} \cellcolor[HTML]{FAC0D8} \\
Dark Magenta & R046 & \texttt{\#C5004F} \cellcolor[HTML]{C5004F} \\
Rose Purple & R048 & \texttt{\#C43BFF} \cellcolor[HTML]{C43BFF} \\
Medium Purple & R049 & \texttt{\#BE00D4} \cellcolor[HTML]{BE00D4} \\
Light Lavender & R052 & \texttt{\#D7BAFF} \cellcolor[HTML]{D7BAFF} \\
Paler Lavender & R053 & \texttt{\#E5DEFF} \cellcolor[HTML]{E5DEFF} \\
Lavender & R058 & \texttt{\#9235FD} \cellcolor[HTML]{9235FD} \\
Mist Blue & R061 & \texttt{\#D6E8FF} \cellcolor[HTML]{D6E8FF} \\
Pale Blue & R063 & \texttt{\#B0D5F7} \cellcolor[HTML]{B0D5F7} \\
Sky Blue & R068 & \texttt{\#597DFF} \cellcolor[HTML]{597DFF} \\
Tokyo Blue & R071 & \texttt{\#3600B1} \cellcolor[HTML]{3600B1} \\
Evening Blue & R075 & \texttt{\#4C79FF} \cellcolor[HTML]{4C79FF} \\
Just Blue & R079 & \texttt{\#3700EB} \cellcolor[HTML]{3700EB} \\
Deeper Blue & R085 & \texttt{\#1A00BF} \cellcolor[HTML]{1A00BF} \\
Lime Green & R088 & \texttt{\#BEFF85} \cellcolor[HTML]{BEFF85} \\
Moss Green & R089 & \texttt{\#00CD55} \cellcolor[HTML]{00CD55} \\
Dark Yellow Green & R090 & \texttt{\#00870B} \cellcolor[HTML]{00870B} \\
Spring Yellow & R100 & \texttt{\#F2FF30} \cellcolor[HTML]{F2FF30} \\
Yellow & R101 & \texttt{\#FFEB0F} \cellcolor[HTML]{FFEB0F} \\
Light Amber & R102 & \texttt{\#FFE74A} \cellcolor[HTML]{FFE74A} \\
Straw & R103 & \texttt{\#FFE7C4} \cellcolor[HTML]{FFE7C4} \\
Deep Amber & R104 & \texttt{\#FCD628} \cellcolor[HTML]{FCD628} \\
Orange & R105 & \texttt{\#FF760D} \cellcolor[HTML]{FF760D} \\
Primary Red & R106 & \texttt{\#DE0000} \cellcolor[HTML]{DE0000} \\
Light Rose & R107 & \texttt{\#FF809F} \cellcolor[HTML]{FF809F} \\
English Rose & R108 & \texttt{\#FAAD96} \cellcolor[HTML]{FAAD96} \\
Light Salmon & R109 & \texttt{\#FF919C} \cellcolor[HTML]{FF919C} \\
Middle Rose & R110 & \texttt{\#FFA3CA} \cellcolor[HTML]{FFA3CA} \\
Dark Pink & R111 & \texttt{\#FF63A4} \cellcolor[HTML]{FF63A4} \\
Magenta & R113 & \texttt{\#FF004D} \cellcolor[HTML]{FF004D} \\
Peacock Blue & R115 & \texttt{\#00C9BF} \cellcolor[HTML]{00C9BF} \\
Medium Blue Green & R116 & \texttt{\#009E96} \cellcolor[HTML]{009E96} \\
Steel Blue & R117 & \texttt{\#A3E2FF} \cellcolor[HTML]{A3E2FF} \\
Light Blue & R118 & \texttt{\#00B7FF} \cellcolor[HTML]{00B7FF} \\
Dark Blue & R119 & \texttt{\#3300D9} \cellcolor[HTML]{3300D9} \\
Deep Blue & R120 & \texttt{\#2800C9} \cellcolor[HTML]{2800C9} \\
Leaf Green & R121 & \texttt{\#93FF54} \cellcolor[HTML]{93FF54} \\
Fern Green & R122 & \texttt{\#74F55D} \cellcolor[HTML]{74F55D} \\
Dark Green & R124 & \texttt{\#00AB44} \cellcolor[HTML]{00AB44} \\
Mauve & R126 & \texttt{\#D400DB} \cellcolor[HTML]{D400DB} \\
Smokey Pink & R127 & \texttt{\#BB334C} \cellcolor[HTML]{BB334C} \\
Bright Pink & R128 & \texttt{\#FF177F} \cellcolor[HTML]{FF177F} \\
Heavy Frost & R129 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Clear & R130 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Marine Blue & R131 & \texttt{\#02E3CC} \cellcolor[HTML]{02E3CC} \\
Medium Blue & R132 & \texttt{\#5286FF} \cellcolor[HTML]{5286FF} \\
Golden Amber & R134 & \texttt{\#F5632F} \cellcolor[HTML]{F5632F} \\
Deep Golden Amber & R135 & \texttt{\#FF4A00} \cellcolor[HTML]{FF4A00} \\
Pale Lavender & R136 & \texttt{\#E2C7FF} \cellcolor[HTML]{E2C7FF} \\
Special Lavender & R137 & \texttt{\#B695FC} \cellcolor[HTML]{B695FC} \\
Pale Green & R138 & \texttt{\#B4FFA8} \cellcolor[HTML]{B4FFA8} \\
Primary Green & R139 & \texttt{\#009107} \cellcolor[HTML]{009107} \\
Summer Blue & R140 & \texttt{\#38CAFF} \cellcolor[HTML]{38CAFF} \\
Bright Blue & R141 & \texttt{\#00ACF0} \cellcolor[HTML]{00ACF0} \\
Pale Violet & R142 & \texttt{\#AA96FF} \cellcolor[HTML]{AA96FF} \\
Pale Navy Blue & R143 & \texttt{\#007194} \cellcolor[HTML]{007194} \\
No Color Blue & R144 & \texttt{\#4FC4FF} \cellcolor[HTML]{4FC4FF} \\
Apricot & R147 & \texttt{\#FF7438} \cellcolor[HTML]{FF7438} \\
Bright Rose & R148 & \texttt{\#FF1472} \cellcolor[HTML]{FF1472} \\
Gold Tint & R151 & \texttt{\#FFC0B5} \cellcolor[HTML]{FFC0B5} \\
Pale Gold & R152 & \texttt{\#FFCAA8} \cellcolor[HTML]{FFCAA8} \\
Pale Salmon & R153 & \texttt{\#FFB2BA} \cellcolor[HTML]{FFB2BA} \\
Pale Rose & R154 & \texttt{\#FFB2BA} \cellcolor[HTML]{FFB2BA} \\
Chocolate & R156 & \texttt{\#C57951} \cellcolor[HTML]{C57951} \\
Pink & R157 & \texttt{\#FF4551} \cellcolor[HTML]{FF4551} \\
Deep Orange & R158 & \texttt{\#FF5E00} \cellcolor[HTML]{FF5E00} \\
No Color Straw & R159 & \texttt{\#FFFAE0} \cellcolor[HTML]{FFFAE0} \\
Slate Blue & R161 & \texttt{\#4AABFF} \cellcolor[HTML]{4AABFF} \\
Bastard Amber & R162 & \texttt{\#FFCFA8} \cellcolor[HTML]{FFCFA8} \\
Flame Red & R164 & \texttt{\#F02225} \cellcolor[HTML]{F02225} \\
Daylight Blue & R165 & \texttt{\#1CACFF} \cellcolor[HTML]{1CACFF} \\
Pale Red & R166 & \texttt{\#FF3352} \cellcolor[HTML]{FF3352} \\
Lilac Tint & R169 & \texttt{\#EBDAF5} \cellcolor[HTML]{EBDAF5} \\
Deep Lavender & R170 & \texttt{\#DAADFF} \cellcolor[HTML]{DAADFF} \\
Lagoon Blue & R172 & \texttt{\#00AACC} \cellcolor[HTML]{00AACC} \\
Dark Steel Blue & R174 & \texttt{\#52B4FF} \cellcolor[HTML]{52B4FF} \\
Loving Amber & R176 & \texttt{\#FAA498} \cellcolor[HTML]{FAA498} \\
Chrome Orange & R179 & \texttt{\#FF9900} \cellcolor[HTML]{FF9900} \\
Dark Lavender & R180 & \texttt{\#8B2BFF} \cellcolor[HTML]{8B2BFF} \\
Congo Blue & R181 & \texttt{\#29007A} \cellcolor[HTML]{29007A} \\
Light Red & R182 & \texttt{\#CC0000} \cellcolor[HTML]{CC0000} \\
Moonlight Blue & R183 & \texttt{\#00BAF2} \cellcolor[HTML]{00BAF2} \\
Cosmetic Peach & R184 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Cosmetic Burgundy & R185 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Cosmetic Silver Rose & R186 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Cosmetic Rouge & R187 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Cosmetic Highlight & R188 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Cosmetic Silver Moss & R189 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Cosmetic Emerald & R190 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Cosmetic Aqua Blue & R191 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Flesh Pink & R192 & \texttt{\#FF639F} \cellcolor[HTML]{FF639F} \\
Rosy Amber & R193 & \texttt{\#FF454B} \cellcolor[HTML]{FF454B} \\
Surprise Pink & R194 & \texttt{\#AC82FF} \cellcolor[HTML]{AC82FF} \\
Zenith Blue & R195 & \texttt{\#0003CC} \cellcolor[HTML]{0003CC} \\
True Blue & R196 & \texttt{\#00A1FF} \cellcolor[HTML]{00A1FF} \\
Alice Blue & R197 & \texttt{\#1958CF} \cellcolor[HTML]{1958CF} \\
Palace Blue & R198 & \texttt{\#43009C} \cellcolor[HTML]{43009C} \\
Regal Blue & R199 & \texttt{\#3700EE} \cellcolor[HTML]{3700EE} \\
Double CT Blue & R200 & \texttt{\#0F5BFF} \cellcolor[HTML]{0F5BFF} \\
Full CT Blue & R201 & \texttt{\#73A9FF} \cellcolor[HTML]{73A9FF} \\
1/2 CT Blue & R202 & \texttt{\#B8D5FF} \cellcolor[HTML]{B8D5FF} \\
1/4 CT Blue & R203 & \texttt{\#E0EDFF} \cellcolor[HTML]{E0EDFF} \\
Full CT Orange & R204 & \texttt{\#FF9B30} \cellcolor[HTML]{FF9B30} \\
1/2 CT Orange & R205 & \texttt{\#FFD28F} \cellcolor[HTML]{FFD28F} \\
1/4 CT Orange & R206 & \texttt{\#FFE6B8} \cellcolor[HTML]{FFE6B8} \\
CT Orange + .3 Neutral Density & R207 & \texttt{\#A86300} \cellcolor[HTML]{A86300} \\
CT Orange + .6 Neutral Density & R208 & \texttt{\#974400} \cellcolor[HTML]{974400} \\
.3 Neutral Density & R209 & \texttt{\#BFBDBD} \cellcolor[HTML]{BFBDBD} \\
.6 Neutral Density & R210 & \texttt{\#969595} \cellcolor[HTML]{969595} \\
.9 Neutral Density & R211 & \texttt{\#636262} \cellcolor[HTML]{636262} \\
LCT Yellow & R212 & \texttt{\#FBFFD9} \cellcolor[HTML]{FBFFD9} \\
White Flame Green & R213 & \texttt{\#E0FCB3} \cellcolor[HTML]{E0FCB3} \\
Full Tough Spun & R214 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Half Tough Spun & R215 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
White Diffusion & R216 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Blue Diffusion & R217 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Eighth CT Blue  & R218 & \texttt{\#EBF3FF} \cellcolor[HTML]{EBF3FF} \\
Fluorescent Green  & R219 & \texttt{\#2EE8CF} \cellcolor[HTML]{2EE8CF} \\
White Frost & R220 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Blue Frost & R221 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
1/8 CT Orange & R223 & \texttt{\#FFEAD1} \cellcolor[HTML]{FFEAD1} \\
Daylight Blue Frost & R224 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Neutral Density Frost & R225 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
U.V. Filter & R226 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Brushed Silk & R228 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Quarter Tough Spun & R229 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Super Correction WF Green & R232 & \texttt{\#AD6824} \cellcolor[HTML]{AD6824} \\
HMI To Tungsten & R236 & \texttt{\#FF8438} \cellcolor[HTML]{FF8438} \\
C.I.D. to Tungsten & R237 & \texttt{\#F08F56} \cellcolor[HTML]{F08F56} \\
C.S.I. to Tungsten & R238 & \texttt{\#E5B1A0} \cellcolor[HTML]{E5B1A0} \\
Polarizer & R239 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Fluorescent 5700K & R241 & \texttt{\#1AD8D8} \cellcolor[HTML]{1AD8D8} \\
Fluorescent 4300K & R242 & \texttt{\#5AE2C7} \cellcolor[HTML]{5AE2C7} \\
Fluorescent 3600K & R243 & \texttt{\#87E5B6} \cellcolor[HTML]{87E5B6} \\
Plus Green & R244 & \texttt{\#E0FC90} \cellcolor[HTML]{E0FC90} \\
Half Plus Green & R245 & \texttt{\#EAFCB8} \cellcolor[HTML]{EAFCB8} \\
Quarter Plus Green & R246 & \texttt{\#F0FCD2} \cellcolor[HTML]{F0FCD2} \\
Minus Green & R247 & \texttt{\#FFB8D0} \cellcolor[HTML]{FFB8D0} \\
Half Minus Green & R248 & \texttt{\#FACDE0} \cellcolor[HTML]{FACDE0} \\
Quarter Minus Green & R249 & \texttt{\#FADEE8} \cellcolor[HTML]{FADEE8} \\
Half White Diffusion & R250 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Quarter White Diffusion & R251 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Eighth White Diffusion & R252 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Hanover Frost & R253 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
HT New Hanover Frost & R254 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Haarlem Frost & R255 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Half Hanover Frost & R256 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Quarter Hanover Frost & R257 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Eighth Hanover Frost & R258 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Heat Shield & R269 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Scrim & R270 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Mirror Silver & R271 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Soft Gold Reflector & R272 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Soft Silver Reflector & R273 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Mirror Gold & R274 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Black Scrim & R275 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Eighth Plus Green & R278 & \texttt{\#F6FFE0} \cellcolor[HTML]{F6FFE0} \\
Eighth Minus Green & R279 & \texttt{\#FCE8F3} \cellcolor[HTML]{FCE8F3} \\
Three Quarter CT Blue & R281 & \texttt{\#9CC5FF} \cellcolor[HTML]{9CC5FF} \\
1.5 CT Blue & R283 & \texttt{\#759EE5} \cellcolor[HTML]{759EE5} \\
3/4 CT Orange & R285 & \texttt{\#F7AF5C} \cellcolor[HTML]{F7AF5C} \\
1.5 CT Orange & R286 & \texttt{\#F8963E} \cellcolor[HTML]{F8963E} \\
Double CT Orange & R287 & \texttt{\#F77F1E} \cellcolor[HTML]{F77F1E} \\
.15 Neutral Density & R298 & \texttt{\#DCD9D9} \cellcolor[HTML]{DCD9D9} \\
1.2 Neutral Density & R299 & \texttt{\#474747} \cellcolor[HTML]{474747} \\
Soft Green & R322 & \texttt{\#02E59A} \cellcolor[HTML]{02E59A} \\
Jade & R323 & \texttt{\#02E2A3} \cellcolor[HTML]{02E2A3} \\
Mallard Green & R325 & \texttt{\#005C46} \cellcolor[HTML]{005C46} \\
Forest Green & R327 & \texttt{\#006539} \cellcolor[HTML]{006539} \\
Follies Pink & R328 & \texttt{\#FF33A0} \cellcolor[HTML]{FF33A0} \\
Special Rose Pink & R332 & \texttt{\#FF0D6A} \cellcolor[HTML]{FF0D6A} \\
Plum & R341 & \texttt{\#CD9BD1} \cellcolor[HTML]{CD9BD1} \\
Special Medium Lavender & R343 & \texttt{\#7345FF} \cellcolor[HTML]{7345FF} \\
Violet & R344 & \texttt{\#A98AFF} \cellcolor[HTML]{A98AFF} \\
Fuschia Pink & R345 & \texttt{\#C953DB} \cellcolor[HTML]{C953DB} \\
Glacier Blue & R352 & \texttt{\#00A6FF} \cellcolor[HTML]{00A6FF} \\
Lighter Blue & R353 & \texttt{\#54D5FF} \cellcolor[HTML]{54D5FF} \\
Special Steel Blue  & R354 & \texttt{\#00BFD8} \cellcolor[HTML]{00BFD8} \\
Special Medium Blue & R363 & \texttt{\#0236DF} \cellcolor[HTML]{0236DF} \\
Cornflower & R366 & \texttt{\#5783CF} \cellcolor[HTML]{5783CF} \\
Rolux & R400 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Light Rolux & R401 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Soft Frost & R402 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Half Soft Frost & R404 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Opal Frost & R410 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Highlight & R414 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Three Quarter White & R416 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Light Opal Frost & R420 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Quiet Frost & R429 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Grid Cloth & R430 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Light Grid Cloth & R432 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Quarter Grid Cloth & R434 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Full CT Straw & R441 & \texttt{\#F7BF4F} \cellcolor[HTML]{F7BF4F} \\
Half CT Straw & R442 & \texttt{\#FFCE9C} \cellcolor[HTML]{FFCE9C} \\
Quarter CT Straw & R443 & \texttt{\#FFE3BA} \cellcolor[HTML]{FFE3BA} \\
Eighth CT Straw & R444 & \texttt{\#FFF5DC} \cellcolor[HTML]{FFF5DC} \\
Three Eighths White & R450 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
One Sixteenth White & R452 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Quiet Grid Cloth & R460 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Quiet Light Grid Cloth & R462 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Quiet Quarter Grid Cloth & R464 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Full Atlantic Frost & R480 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Half Atlantic Frost & R481 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Quarter Atlantic Frost & R482 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Double New Colour Blue & R500 & \texttt{\#6977FF} \cellcolor[HTML]{6977FF} \\
New Colour Blue (Robertson Blue) & R501 & \texttt{\#BFC7FB} \cellcolor[HTML]{BFC7FB} \\
Half New Colour Blue & R502 & \texttt{\#D9E3FF} \cellcolor[HTML]{D9E3FF} \\
Quarter New Colour Blue & R503 & \texttt{\#F0F5FF} \cellcolor[HTML]{F0F5FF} \\
Waterfront Green & R504 & \texttt{\#B3DCE3} \cellcolor[HTML]{B3DCE3} \\
Sally Green & R505 & \texttt{\#BFFF59} \cellcolor[HTML]{BFFF59} \\
Marlene & R506 & \texttt{\#F7C9A3} \cellcolor[HTML]{F7C9A3} \\
Madge & R507 & \texttt{\#E93511} \cellcolor[HTML]{E93511} \\
Midnight Maya & R508 & \texttt{\#1602AA} \cellcolor[HTML]{1602AA} \\
Argent Blue & R525 & \texttt{\#2261D6} \cellcolor[HTML]{2261D6} \\
Gold Medal & R550 & \texttt{\#F5AE3F} \cellcolor[HTML]{F5AE3F} \\
Full CT Eight Five & R604 & \texttt{\#FFC470} \cellcolor[HTML]{FFC470} \\
Half Mustard Yellow & R642 & \texttt{\#DFAB00} \cellcolor[HTML]{DFAB00} \\
Quarter Mustard Yellow & R643 & \texttt{\#FDC200} \cellcolor[HTML]{FDC200} \\
Industry Sodium & R650 & \texttt{\#D9CE73} \cellcolor[HTML]{D9CE73} \\
HI Sodium & R651 & \texttt{\#FFB95C} \cellcolor[HTML]{FFB95C} \\
Urban Sodium & R652 & \texttt{\#FF752B} \cellcolor[HTML]{FF752B} \\
LO Sodium & R653 & \texttt{\#5E2A02} \cellcolor[HTML]{5E2A02} \\
Perfect Lavender & R700 & \texttt{\#7500EB} \cellcolor[HTML]{7500EB} \\
Provence & R701 & \texttt{\#9A3BFF} \cellcolor[HTML]{9A3BFF} \\
Special Pale Lavender & R702 & \texttt{\#DACCFF} \cellcolor[HTML]{DACCFF} \\
Cold Lavender & R703 & \texttt{\#C587FF} \cellcolor[HTML]{C587FF} \\
Lily & R704 & \texttt{\#E2BAFF} \cellcolor[HTML]{E2BAFF} \\
Lily Frost & R705 & \texttt{\#D59EFF} \cellcolor[HTML]{D59EFF} \\
King Fals Lavender & R706 & \texttt{\#6600FF} \cellcolor[HTML]{6600FF} \\
Ultimate Violet & R707 & \texttt{\#7500F2} \cellcolor[HTML]{7500F2} \\
Cool Lavender & R708 & \texttt{\#BFC8FF} \cellcolor[HTML]{BFC8FF} \\
Electric Lilac & R709 & \texttt{\#7394FF} \cellcolor[HTML]{7394FF} \\
Spir Special Blue & R710 & \texttt{\#554CFF} \cellcolor[HTML]{554CFF} \\
Cold Blue & R711 & \texttt{\#224ED4} \cellcolor[HTML]{224ED4} \\
Bedford Blue & R712 & \texttt{\#3853FF} \cellcolor[HTML]{3853FF} \\
Winter Blue & R713 & \texttt{\#1F009A} \cellcolor[HTML]{1F009A} \\
Elysian Blue & R714 & \texttt{\#0F17FF} \cellcolor[HTML]{0F17FF} \\
Cabanna Blue & R715 & \texttt{\#072EDE} \cellcolor[HTML]{072EDE} \\
Mikkel Blue & R716 & \texttt{\#2600BF} \cellcolor[HTML]{2600BF} \\
Shanklin Frost & R717 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
1/2 Shanklin Frost & R718 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Colour Wash Blue & R719 & \texttt{\#2265F5} \cellcolor[HTML]{2265F5} \\
Daylight Frost & R720 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Berry Blue & R721 & \texttt{\#0036E8} \cellcolor[HTML]{0036E8} \\
Bray Blue & R722 & \texttt{\#0024C2} \cellcolor[HTML]{0024C2} \\
Virgin Blue & R723 & \texttt{\#0031F7} \cellcolor[HTML]{0031F7} \\
Ocean Blue & R724 & \texttt{\#2BC7FF} \cellcolor[HTML]{2BC7FF} \\
Old Steel Blue & R725 & \texttt{\#8CDFFF} \cellcolor[HTML]{8CDFFF} \\
QFD Blue & R727 & \texttt{\#007385} \cellcolor[HTML]{007385} \\
Steel Green & R728 & \texttt{\#95DEDA} \cellcolor[HTML]{95DEDA} \\
Scuba Blue & R729 & \texttt{\#007070} \cellcolor[HTML]{007070} \\
Liberty Green & R730 & \texttt{\#A3F7DB} \cellcolor[HTML]{A3F7DB} \\
Dirty Ice & R731 & \texttt{\#B4F0D2} \cellcolor[HTML]{B4F0D2} \\
Damp Squib & R733 & \texttt{\#A8E5C7} \cellcolor[HTML]{A8E5C7} \\
Velvet Green & R735 & \texttt{\#005C1D} \cellcolor[HTML]{005C1D} \\
Twickenham Green & R736 & \texttt{\#0D5700} \cellcolor[HTML]{0D5700} \\
Jas Green & R738 & \texttt{\#5FE300} \cellcolor[HTML]{5FE300} \\
Aurora Borealis Green & R740 & \texttt{\#354D15} \cellcolor[HTML]{354D15} \\
Mustard Yellow & R741 & \texttt{\#C5A100} \cellcolor[HTML]{C5A100} \\
Bram Brown & R742 & \texttt{\#8E5324} \cellcolor[HTML]{8E5324} \\
Dirty White & R744 & \texttt{\#F7C757} \cellcolor[HTML]{F7C757} \\
Brown  & R746 & \texttt{\#753900} \cellcolor[HTML]{753900} \\
Easy White & R747 & \texttt{\#CC8C7C} \cellcolor[HTML]{CC8C7C} \\
Seedy Pink & R748 & \texttt{\#C23061} \cellcolor[HTML]{C23061} \\
Hanover Rose & R749 & \texttt{\#FFBCBA} \cellcolor[HTML]{FFBCBA} \\
Durham Frost & R750 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Wheat & R763 & \texttt{\#FFEFBA} \cellcolor[HTML]{FFEFBA} \\
Sun Colour Straw & R764 & \texttt{\#FFEC94} \cellcolor[HTML]{FFEC94} \\
Sunlight Yellow & R765 & \texttt{\#FFEC6E} \cellcolor[HTML]{FFEC6E} \\
Oklahoma Yellow & R767 & \texttt{\#FFDE24} \cellcolor[HTML]{FFDE24} \\
Egg Yolk Yellow & R768 & \texttt{\#FCC200} \cellcolor[HTML]{FCC200} \\
Burnt Yellow & R770 & \texttt{\#FF8A0D} \cellcolor[HTML]{FF8A0D} \\
Cardbox Amber & R773 & \texttt{\#FFB28F} \cellcolor[HTML]{FFB28F} \\
Soft Amber & R774 & \texttt{\#FFC49C} \cellcolor[HTML]{FFC49C} \\
Soft Amber 2 & R775 & \texttt{\#FFBA8C} \cellcolor[HTML]{FFBA8C} \\
Nectarine & R776 & \texttt{\#FF8345} \cellcolor[HTML]{FF8345} \\
Rust & R777 & \texttt{\#D94F18} \cellcolor[HTML]{D94F18} \\
Millennium Gold & R778 & \texttt{\#FF4405} \cellcolor[HTML]{FF4405} \\
Bastard Pink & R779 & \texttt{\#F56A2F} \cellcolor[HTML]{F56A2F} \\
As Golden Amber & R780 & \texttt{\#FF3B05} \cellcolor[HTML]{FF3B05} \\
Terry Red & R781 & \texttt{\#FF0F0D} \cellcolor[HTML]{FF0F0D} \\
Marius Red & R787 & \texttt{\#91001B} \cellcolor[HTML]{91001B} \\
Blood Red & R789 & \texttt{\#99000D} \cellcolor[HTML]{99000D} \\
Moroccan Pink & R790 & \texttt{\#FF919C} \cellcolor[HTML]{FF919C} \\
Moroccan Frost & R791 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Vanity Fair & R793 & \texttt{\#FF12AC} \cellcolor[HTML]{FF12AC} \\
Pretty N Pink & R794 & \texttt{\#FF82DE} \cellcolor[HTML]{FF82DE} \\
Magical Magenta & R795 & \texttt{\#FF00C8} \cellcolor[HTML]{FF00C8} \\
Deep Purple & R797 & \texttt{\#AD00CC} \cellcolor[HTML]{AD00CC} \\
Chrysalis Pink & R798 & \texttt{\#7B0FFF} \cellcolor[HTML]{7B0FFF} \\
Special K.H. Lavender & R799 & \texttt{\#120096} \cellcolor[HTML]{120096} \\
Damson Violet & R5084 & \texttt{\#8800C7} \cellcolor[HTML]{8800C7} \\
French Lilac & R5085 & \texttt{\#6D00F2} \cellcolor[HTML]{6D00F2} \\
Max Blue & R5202 & \texttt{\#B8D4FF} \cellcolor[HTML]{B8D4FF} \\
Ice Blue & R5211 & \texttt{\#E8F4FF} \cellcolor[HTML]{E8F4FF} \\
Venetian Blue & R5264 & \texttt{\#96C9FF} \cellcolor[HTML]{96C9FF} \\
Fuji Blue & R5287 & \texttt{\#002DE3} \cellcolor[HTML]{002DE3} \\
Aztec Gold & R5336 & \texttt{\#F2CF88} \cellcolor[HTML]{F2CF88} \\
Wisteria & R5404 & \texttt{\#DFCFFF} \cellcolor[HTML]{DFCFFF} \\
Olympia Green & R5454 & \texttt{\#009C72} \cellcolor[HTML]{009C72} \\
Tarragon & R5455 & \texttt{\#7DFFB1} \cellcolor[HTML]{7DFFB1} \\
Grotto Green & R5461 & \texttt{\#02BF9C} \cellcolor[HTML]{02BF9C} \\
Prussian Green & R5463 & \texttt{\#00A6B5} \cellcolor[HTML]{00A6B5} \\
\hline
\end{longtable}
\subsubsection{Supergel}
\begin{longtable}{|l|l|r|}
\hline
Gel Name & Manufacturer Code & Rendered Colour \\ \hline
Dempster Open White & S00 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Light Bastard Amber & S01 & \texttt{\#FBB39A} \cellcolor[HTML]{FBB39A} \\
Bastard Amber & S02 & \texttt{\#FFD1AC} \cellcolor[HTML]{FFD1AC} \\
Dark Bastard Amber & S03 & \texttt{\#FBBA9A} \cellcolor[HTML]{FBBA9A} \\
Warm Peach & S303 & \texttt{\#FF8A4A} \cellcolor[HTML]{FF8A4A} \\
Medium Bastard Amber & S04 & \texttt{\#F9B09A} \cellcolor[HTML]{F9B09A} \\
Pale Apricot & S304 & \texttt{\#FABCA9} \cellcolor[HTML]{FABCA9} \\
Rose Tint & S05 & \texttt{\#FFD7D3} \cellcolor[HTML]{FFD7D3} \\
Rose Gold & S305 & \texttt{\#F5BAB8} \cellcolor[HTML]{F5BAB8} \\
No Color Straw & S06 & \texttt{\#FCFADB} \cellcolor[HTML]{FCFADB} \\
Pale Yellow  & S07 & \texttt{\#FDFAD1} \cellcolor[HTML]{FDFAD1} \\
Pale Amber Gold & S09 & \texttt{\#FFCB86} \cellcolor[HTML]{FFCB86} \\
Medium Yellow & S10 & \texttt{\#FFF200} \cellcolor[HTML]{FFF200} \\
Light Straw & S11 & \texttt{\#FFD21A} \cellcolor[HTML]{FFD21A} \\
Canary & S312 & \texttt{\#FFEA00} \cellcolor[HTML]{FFEA00} \\
Straw Tint  & S13 & \texttt{\#FFD88F} \cellcolor[HTML]{FFD88F} \\
Light Relief Yellow & S313 & \texttt{\#FFE462} \cellcolor[HTML]{FFE462} \\
Medium Straw & S14 & \texttt{\#FCD419} \cellcolor[HTML]{FCD419} \\
Deep Straw  & S15 & \texttt{\#FECB00} \cellcolor[HTML]{FECB00} \\
Apricot & S317 & \texttt{\#FF7418} \cellcolor[HTML]{FF7418} \\
Mayan Sun & S318 & \texttt{\#FF6F29} \cellcolor[HTML]{FF6F29} \\
Fire & S19 & \texttt{\#FF390B} \cellcolor[HTML]{FF390B} \\
Medium Amber & S20 & \texttt{\#FF871C} \cellcolor[HTML]{FF871C} \\
Golden Amber & S21 & \texttt{\#FF6613} \cellcolor[HTML]{FF6613} \\
Deep Amber & S22 & \texttt{\#FF430A} \cellcolor[HTML]{FF430A} \\
Orange & S23 & \texttt{\#FF5A00} \cellcolor[HTML]{FF5A00} \\
Scarlet & S24 & \texttt{\#F50014} \cellcolor[HTML]{F50014} \\
Gypsy Red & S324 & \texttt{\#F50F39} \cellcolor[HTML]{F50F39} \\
Orange Red & S25 & \texttt{\#E51F00} \cellcolor[HTML]{E51F00} \\
Light Red & S26 & \texttt{\#D70229} \cellcolor[HTML]{D70229} \\
Medium Red & S27 & \texttt{\#B00202} \cellcolor[HTML]{B00202} \\
Light Salmon Pink & S30 & \texttt{\#FF7A59} \cellcolor[HTML]{FF7A59} \\
Salmon Pink & S31 & \texttt{\#FF847F} \cellcolor[HTML]{FF847F} \\
Shell Pink & S331 & \texttt{\#FF9D8D} \cellcolor[HTML]{FF9D8D} \\
Medium Salmon Pink & S32 & \texttt{\#FF413C} \cellcolor[HTML]{FF413C} \\
Cherry Rose & S332 & \texttt{\#FF2957} \cellcolor[HTML]{FF2957} \\
No Color Pink & S33 & \texttt{\#FFC2D0} \cellcolor[HTML]{FFC2D0} \\
Light Pink & S35 & \texttt{\#FFA7BB} \cellcolor[HTML]{FFA7BB} \\
Medium Pink & S36 & \texttt{\#FF6D96} \cellcolor[HTML]{FF6D96} \\
Billington Pink & S336 & \texttt{\#FF73B7} \cellcolor[HTML]{FF73B7} \\
True Pink & S337 & \texttt{\#FFAFC2} \cellcolor[HTML]{FFAFC2} \\
Light Rose & S38 & \texttt{\#FFBBE2} \cellcolor[HTML]{FFBBE2} \\
Broadway Pink & S339 & \texttt{\#FF1283} \cellcolor[HTML]{FF1283} \\
Skelton Exotic Sangria & S39 & \texttt{\#E800BC} \cellcolor[HTML]{E800BC} \\
Light Salmon & S40 & \texttt{\#FF4F1F} \cellcolor[HTML]{FF4F1F} \\
Rose Pink & S342 & \texttt{\#FF1562} \cellcolor[HTML]{FF1562} \\
Deep Pink & S43 & \texttt{\#FF3E93} \cellcolor[HTML]{FF3E93} \\
Neon Pink & S343 & \texttt{\#FF397F} \cellcolor[HTML]{FF397F} \\
Follies Pink & S344 & \texttt{\#FF05D3} \cellcolor[HTML]{FF05D3} \\
Rose & S45 & \texttt{\#EB016D} \cellcolor[HTML]{EB016D} \\
Magenta & S46 & \texttt{\#BD045D} \cellcolor[HTML]{BD045D} \\
Tropical Magenta & S346 & \texttt{\#FF2DD5} \cellcolor[HTML]{FF2DD5} \\
Light Rose Purple & S47 & \texttt{\#CC4EB9} \cellcolor[HTML]{CC4EB9} \\
Belladonna Rose & S347 & \texttt{\#B101DD} \cellcolor[HTML]{B101DD} \\
Rose Purple & S48 & \texttt{\#C800CF} \cellcolor[HTML]{C800CF} \\
Purple Jazz & S348 & \texttt{\#DA2DFF} \cellcolor[HTML]{DA2DFF} \\
Medium Purple & S49 & \texttt{\#C900E6} \cellcolor[HTML]{C900E6} \\
Fisher Fuchsia & S349 & \texttt{\#F000FF} \cellcolor[HTML]{F000FF} \\
Mauve & S50 & \texttt{\#BB002C} \cellcolor[HTML]{BB002C} \\
Lavender Mist & S351 & \texttt{\#EFDCFF} \cellcolor[HTML]{EFDCFF} \\
Light Lavender & S52 & \texttt{\#DDBFFF} \cellcolor[HTML]{DDBFFF} \\
Pale Lavender & S53 & \texttt{\#E4DCFF} \cellcolor[HTML]{E4DCFF} \\
Lilly Lavender & S353 & \texttt{\#C4ADFF} \cellcolor[HTML]{C4ADFF} \\
Special Lavender & S54 & \texttt{\#E6C7FF} \cellcolor[HTML]{E6C7FF} \\
Lilac & S55 & \texttt{\#C0AAFD} \cellcolor[HTML]{C0AAFD} \\
Pale Violet & S355 & \texttt{\#A590FF} \cellcolor[HTML]{A590FF} \\
Gypsy Lavender & S56 & \texttt{\#8C2FFF} \cellcolor[HTML]{8C2FFF} \\
Middle Lavender & S356 & \texttt{\#C38DFF} \cellcolor[HTML]{C38DFF} \\
Lavender & S57 & \texttt{\#B482FF} \cellcolor[HTML]{B482FF} \\
Royal Lavender & S357 & \texttt{\#8A2BFF} \cellcolor[HTML]{8A2BFF} \\
Deep Lavender & S58 & \texttt{\#933FFD} \cellcolor[HTML]{933FFD} \\
Rose Indigo & S358 & \texttt{\#8E0AEA} \cellcolor[HTML]{8E0AEA} \\
Indigo & S59 & \texttt{\#7200FF} \cellcolor[HTML]{7200FF} \\
Medium Violet & S359 & \texttt{\#683FFF} \cellcolor[HTML]{683FFF} \\
Mist Blue & S61 & \texttt{\#D3EAFF} \cellcolor[HTML]{D3EAFF} \\
Hemsley Blue & S361 & \texttt{\#669EFC} \cellcolor[HTML]{669EFC} \\
Booster Blue & S62 & \texttt{\#A1CEFF} \cellcolor[HTML]{A1CEFF} \\
Pale Blue & S63 & \texttt{\#A4D3FF} \cellcolor[HTML]{A4D3FF} \\
Aquamarine & S363 & \texttt{\#ABE9FF} \cellcolor[HTML]{ABE9FF} \\
Light Steel Blue & S64 & \texttt{\#50AEFD} \cellcolor[HTML]{50AEFD} \\
Daylight Blue & S65 & \texttt{\#00A9FF} \cellcolor[HTML]{00A9FF} \\
Cool Blue & S66 & \texttt{\#94EAFF} \cellcolor[HTML]{94EAFF} \\
Jordan Blue & S366 & \texttt{\#29C0F9} \cellcolor[HTML]{29C0F9} \\
Light Sky Blue & S67 & \texttt{\#14A9FF} \cellcolor[HTML]{14A9FF} \\
Slate Blue & S367 & \texttt{\#44A5FF} \cellcolor[HTML]{44A5FF} \\
Parry Sky Blue & S68 & \texttt{\#447DFF} \cellcolor[HTML]{447DFF} \\
Winkler Blue & S368 & \texttt{\#448AFF} \cellcolor[HTML]{448AFF} \\
Brilliant Blue & S69 & \texttt{\#00A3F7} \cellcolor[HTML]{00A3F7} \\
Tahitian Blue & S369 & \texttt{\#00C6FF} \cellcolor[HTML]{00C6FF} \\
Nile Blue & S70 & \texttt{\#6CE5FF} \cellcolor[HTML]{6CE5FF} \\
Italian Blue & S370 & \texttt{\#01CDDF} \cellcolor[HTML]{01CDDF} \\
Sea Blue & S71 & \texttt{\#0096C7} \cellcolor[HTML]{0096C7} \\
Theatre Booster 1 & S371 & \texttt{\#A3A8FF} \cellcolor[HTML]{A3A8FF} \\
Azure Blue & S72 & \texttt{\#55CCFF} \cellcolor[HTML]{55CCFF} \\
Theatre Booster 2 & S372 & \texttt{\#D9DCFF} \cellcolor[HTML]{D9DCFF} \\
Peacock Blue & S73 & \texttt{\#00A4B8} \cellcolor[HTML]{00A4B8} \\
Theatre Booster 3 & S373 & \texttt{\#E0E9FD} \cellcolor[HTML]{E0E9FD} \\
Night Blue & S74 & \texttt{\#4200FF} \cellcolor[HTML]{4200FF} \\
Sea Green & S374 & \texttt{\#01A4A6} \cellcolor[HTML]{01A4A6} \\
Twilight Blue & S75 & \texttt{\#007AAC} \cellcolor[HTML]{007AAC} \\
Light Green Blue & S76 & \texttt{\#005773} \cellcolor[HTML]{005773} \\
Iris Purple & S377 & \texttt{\#7124FF} \cellcolor[HTML]{7124FF} \\
Trudy Blue & S78 & \texttt{\#6F6FFF} \cellcolor[HTML]{6F6FFF} \\
Bright Blue & S79 & \texttt{\#1626FF} \cellcolor[HTML]{1626FF} \\
Primary Blue & S80 & \texttt{\#0048FF} \cellcolor[HTML]{0048FF} \\
Urban Blue & S81 & \texttt{\#486FFF} \cellcolor[HTML]{486FFF} \\
Surprise Blue & S82 & \texttt{\#4F34F8} \cellcolor[HTML]{4F34F8} \\
Congo Blue & S382 & \texttt{\#250070} \cellcolor[HTML]{250070} \\
Medium Blue & S83 & \texttt{\#0228EC} \cellcolor[HTML]{0228EC} \\
Sapphire Blue & S383 & \texttt{\#0022D1} \cellcolor[HTML]{0022D1} \\
Zephyr Blue & S84 & \texttt{\#5767FF} \cellcolor[HTML]{5767FF} \\
Midnight Blue & S384 & \texttt{\#0500D0} \cellcolor[HTML]{0500D0} \\
Deep Blue & S85 & \texttt{\#0049CE} \cellcolor[HTML]{0049CE} \\
Royal Blue & S385 & \texttt{\#4F02CF} \cellcolor[HTML]{4F02CF} \\
Pea Green & S86 & \texttt{\#89FA19} \cellcolor[HTML]{89FA19} \\
Leaf Green & S386 & \texttt{\#7BD300} \cellcolor[HTML]{7BD300} \\
Gaslight Green & S388 & \texttt{\#D0F54E} \cellcolor[HTML]{D0F54E} \\
Moss Green & S89 & \texttt{\#51F655} \cellcolor[HTML]{51F655} \\
Chroma Green & S389 & \texttt{\#29F433} \cellcolor[HTML]{29F433} \\
Dark Yellow Green & S90 & \texttt{\#007F06} \cellcolor[HTML]{007F06} \\
Primary Green & S91 & \texttt{\#005E2C} \cellcolor[HTML]{005E2C} \\
Pacific Green & S392 & \texttt{\#009493} \cellcolor[HTML]{009493} \\
Blue Green & S93 & \texttt{\#01A3A0} \cellcolor[HTML]{01A3A0} \\
Emerald Green & S393 & \texttt{\#007150} \cellcolor[HTML]{007150} \\
Kelly Green & S94 & \texttt{\#00985D} \cellcolor[HTML]{00985D} \\
Medium Blue Green & S95 & \texttt{\#009C91} \cellcolor[HTML]{009C91} \\
Teal Green & S395 & \texttt{\#00726A} \cellcolor[HTML]{00726A} \\
Lime & S96 & \texttt{\#F3FF6B} \cellcolor[HTML]{F3FF6B} \\
Neutral Grey & S398 & \texttt{\#B0B4B9} \cellcolor[HTML]{B0B4B9} \\
Frost & S100 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Light Frost & S101 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Tough Silk & S104 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Matte Silk & S113 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Hamburg Frost & S114 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Light Hamburg Frost & S119 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Red Diffusion & S120 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Blue Diffusion & S121 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Green Diffusion & S122 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Red Cyc Silk & S124 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Blue Cyc Silk & S125 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Green Cyc Silk & S126 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Amber Cyc Silk & S127 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Quarter Hamburg Frost & S132 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Subtle Hamburg Frost & S140 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
Light Tough Silk & S160 & \texttt{\#FFFFFF} \cellcolor[HTML]{FFFFFF} \\
\hline
\end{longtable}

\end{document}
